What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-05 thesis/proposal_draft.Rmd
update appendix

Looking at the plots of the monthly aggregates, we can inspect the data quickly for obvious outliers. After detrending the time series for both the deterministic trends (non-zero mean) and stochastic trends (weekly and daily cycles), we expect to have stationary series.

>>>>

Looking at the plots of the monthly aggregates, we can inspect the data quickly for obvious outliers. After detrending the time series for both the deterministic trends (non-zero mean) and stochastic trends (weekly and daily cycles), we expect to have a stationary series. Anything outside these "expected" trends from the cycles could indicate an unobserved variable (such as weather) having a casual effect on the pedestrian count. Large "dips" in the series, or odd values over a long time span may be indicative of missing values which need to be imputed.
